% Bibliography

\label{app:bibliography} % Reference the bibliography elsewhere with \autoref{app:bibliography}

\manualmark
\markboth{\spacedlowsmallcaps{\bibname}}{\spacedlowsmallcaps{\bibname}} 
\refstepcounter{dummy}

\addtocontents{toc}{\protect\vspace{\beforebibskip}} % Place the bibliography slightly below the rest of the document content in the table of contents
\addcontentsline{toc}{chapter}{\tocEntry{\bibname}}

\bibliographystyle{plainnat}

\bibliography{FrontBackMatter/Bibliography}

\begin{thebibliography}{99}

\bibitem{simbad}
SIMBAD Astronomical Database, http://simbad.u-strasbg.fr/simbad/

\bibitem{Masetti}
Masetti, N., Mason, E.,  Morelli, L., et al., Unveiling the nature of INTEGRAL objects through optical spectroscopy, Astronomy & Astrophysics, no. 482, pg. 113-132 (2008).

\bibitem{Mason}
Mason, A.B., Norton A.J., et al., The masses of the neutron and donor star in the high-mass X-ray binary IGR J18027-2016, Astronomy & Astrophysics, no. 532, Article 124 (2011).

\bibitem{Seward}
Seward, F.D. and Charles, P.A., Exploring the X-ray Universe, Cambridge University Press, ISBN 978-0521884839

\bibitem{Goldwurm}
Goldwurm A. et. al, Gamma-Ray Imaging with the Coded Mask IBIS Telescope, http://arxiv.org/abs/astro-ph/0102386, February 2001

\bibitem{Sidoli}
Sidoli, L. et. al., The XMM–Newton view of supergiant fast X-ray transients: the case of IGR J16418-4532, Monthly Notices of the Royal Astronomical Society, Vol 420, Issue 1, pages 554-561, February 2012

\bibitem{Romano}
Romano, P. et. al., Swift/X-ray Telescope monitoring of the candidate supergiant fast X-ray transient IGR J16418-4532, Monthly Notices of the Royal Astronomical Society Volume 419, Issue 3, pages 2695-2702, January 2012


\end{thebibliography}